Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
Unc example
Updated experiments result table.

$$
\begin{array}{ll}
N_C(z) {=} 0z^2{+}0z{+}0\\
D_C(z) {=} 0z^2{+}0z{+}0\\
\end{array}
$$

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\begin{array}{ll}
N_C(z) {=} 12.402664z^2{-}11.439667z{+}0.596756\\
D_C(z) {=} 4.003906z^2{-}0.287949z{+}0.015625\\
\end{array}
$$

@@

$$
\begin{array}{ll}
N_C(z) {=} 11.035202z^2{+}5.846100z{+}4.901855\\
D_C(z) {=} 1.097901z^2{+}0.063110z{+}0.128357\\
\end{array}
$$

@@

\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example. Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase. The resulting controller is
}

@@

\begin{figure}[H]
\centering
\begin{tabular}{l | r r l}
Benchmark              & Base     & Unc     & \\\cline{1-4}
CruiseControl02        & 17\,s    & 46\,s   & \\
SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
SpringMassDamper       & 28\,s    & \xmark  &
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
\vspace{0.5em}

\caption{Experimental results. \textcolor{red}{It should be a table and not a figure.} \label{tab:results}}
\end{figure}
%---------------------------------

>>>>

%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$
\blue{
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
}
$$

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\blue{
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
}
$$

@@

$$
\blue{
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
}
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

@@

\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example. Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase. The resulting controller is:
}
$$
{
\blue{
C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
}}
$$

\blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
$$
{
\blue{
C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
}}
$$

@@

\begin{table}[H]
\centering
\begin{tabular}{l | r l}
Benchmark                 & Base    & \\\cline{1-2}
CruiseControl02           & 17\,s   & \\
CruiseControl02$^\dagger$ & 46\,s   & \\
SatelliteB2               & 7\,s    & \\
SatelliteB2$^\dagger$     & 6601\,s & \tbmark\\
SatelliteC2               & 2\,s    & \\
SatelliteC2$^\dagger$     & 76\,s   & \tbmark\\
SpringMassDamper          & 28\,s   & \\
a\_PL1\_SCH2\_IMPL1       & 2704\,s & \\
a\_PL1\_SCH2\_IMPL2       & 538\,s  & \\
a\_PL1\_SCH2\_IMPL3       & 12\,s   & \\
a\_PL1\_SCH3\_IMPL1       & 318\,s  & \\
a\_PL1\_SCH3\_IMPL2       & 967\,s  & \\
a\_PL1\_SCH3\_IMPL3       & 9798\,s & \\
a\_PL1\_SCH4\_IMPL1       & 6304\,s & \\
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end, $\dagger$ = with uncertainty}
\vspace{0.5em}

\caption{Experimental results. \label{tab:results}}
\end{table}
%---------------------------------
